Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion.tex
edits in Theorem 10
edits to Theorem 10

The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential (in \ARMNUM) payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
In this section, we discuss two restrictions on the problem setting under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
Both problem settings are special cases of the more general problem setting previously considered.

\subsubsection{Discrete Preferences}
\label{subsec:discrete}
Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):

\begin{assumption}[Discrete Preferences]
\label{a:discrete}
There is a positive $\delta_0$ such that
$\AlmostTied{\delta_0} = 0$.
\end{assumption}

When Assumption~\ref{a:discrete} holds, we restrict the payment-eligibility criterion by only incentivizing arms with much smaller probability to be pulled: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
\end{itemize}

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{theorem}

@@

When this assumption holds, we choose a different modification in the definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both of the following hold:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

@@

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
\end{theorem}

>>>>

The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret}
incur exponential (in \ARMNUM) payment and regret in the initial
phases because the threshold $1/\log(s)$ required for incentivization
decreases slowly. 
This slow decrease is needed to bound the regret in the later phases
when the concentration inequality kicks in as in
Equation~(\ref{equ:small_regret_bound}).
In this section, we discuss two restrictions under which we can
modify the algorithm slightly and provide stronger bounds,
avoiding this exponential dependence.
Both problem settings are special cases of the more general
setting previously considered.

\subsubsection{Discrete Preferences}
\label{subsec:discrete}
Discrete preferences by agents are captured by the following
\dkedit{strengthening of Assumption~\ref{A1}},
which states that the agents who are close to tied between
two arms have measure 0:

\begin{assumption}[Discrete Preferences]
\label{a:discrete}
There is a positive $\hat{z}$ such that
$\AlmostTied{\hat{z}} = 0$.
\end{assumption}

When Assumption~\ref{a:discrete} holds,
we restrict the payment-eligibility criterion by only incentivizing
arms with much smaller probability to be pulled:
an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
the following are true:

\begin{itemize}
\item $i$ has been pulled at most $s$ times up to time $t$,
i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
the probability of pulling arm $i$ is less than $1/s$
(compared to $1/\log(s)$ in the general algorithm).
\end{itemize}

@@

\begin{theorem}
\label{rst:discrete}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
has expected payment bounded above by 
$O \left(\ARMNUM^2/\MinProb \right)$
and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
\end{theorem}

@@

When this assumption holds, we choose a different modification in the
definition of payment eligibility.
Let $s_0 = \exp(2/\MinProb)$.
An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
if both:
\begin{itemize}
\item $i$ has been pulled at most
$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
\end{itemize}

@@

\begin{theorem}
\label{rst:known-p}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
expected payment  bounded above by  
$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
and expected regret bounded above by
%\begin{align*}
\dkedit{$O \left( \frac{\ARMNUM^2}{\MinProb^2}
%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$}.
%  \end{align*}
\end{theorem}
